---
title: "Text Mining of HappyDB"
author: "Shengjie Sun (ss5593)"
date: "February 6, 2019"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparation

### Step 0 - Load all the required Libraries

```{r load libraries, warning=FALSE, message=FALSE}
library(tidytext)
library(tidyverse)
library(tidyr)
library(tm)

library(topicmodels)
library(LDAvis)
library(slam)
library(servr)
library(gridExtra)
library(ggridges)
```

### Step 1 - Load the cleaned and processed data

Considering the conciseness, all of the text preprocessing part are done in `Text_Processing_Modified.rmd` and the data we use here is called `processed_moments_modified.csv` saved in `output`. 

```{r read data, warning=FALSE, message=FALSE}
hm_tbl <- read.csv("../output/processed_moments_modified.csv", stringsAsFactors=FALSE) %>% as.tibble()
hm_tbl_re <- hm_tbl %>% mutate(age = ifelse(age >= 75, 75, age))

Corpus <- hm_tbl_re$text %>% VectorSource() %>% VCorpus()
dtm <- Corpus %>% DocumentTermMatrix()
```

## Happiness V.S. Age
- Motivation: Happiness is a kind of emotion of people while the age is a character that changes with the time goes by. With the increasing of age, the knowledge, status and personality will change dynamically. 
- Goal: The main goal of this part is to analysis, how the pattern of happiness changes with the increasing of age.

### Question 1 - Demographic bias
```{r Create the demographic tibble, warning=FALSE, message=FALSE}
dem_tbl <- hm_tbl %>% count(age, gender, marital, parenthood)
dem_tbl_re <- dem_tbl %>% mutate(age = ifelse(age >= 75, 75, age))
```

```{r, warning=FALSE, message=FALSE}
dem_tbl %>% 
  group_by(age, gender) %>% 
  summarise(percent = sum(n)) %>% 
  mutate(percent = percent/sum(percent)) %>%
  ggplot(aes(x = age, y = percent, fill = gender)) + 
  geom_col(position = "stack", width=0.8)
```

```{r, warning=FALSE, message=FALSE}
dem_tbl_re %>% 
  group_by(age, gender) %>% 
  summarise(percent = sum(n)) %>% 
  mutate(percent = percent/sum(percent)) %>%
  ggplot(aes(x = age, y = percent, fill = gender)) + 
  geom_col(position = "stack", width=0.87)
```
```{r, warning=FALSE, message=FALSE}
dem_tbl_re %>% 
  group_by(age, marital) %>% 
  summarise(percent = sum(n)) %>% 
  mutate(percent = percent/sum(percent)) %>%
  ggplot(aes(x = age, y = percent, fill = marital)) + 
  geom_col(position = "stack", width=0.8)
```
```{r, warning=FALSE, message=FALSE}
dem_tbl_re %>% 
  group_by(age, parenthood) %>% 
  summarise(percent = sum(n)) %>% 
  mutate(percent = percent/sum(percent)) %>%
  ggplot(aes(x = age, y = percent, fill = parenthood)) + 
  geom_col(position = "stack", width=0.87)
```

### Question 2 - Single Value Index
```{r, warning=FALSE, message=FALSE}
hm_token <- hm_tbl_re %>%
  unnest_tokens(word, text) %>%
  inner_join(get_sentiments("afinn"), by="word") %>%
  mutate(score = abs(score))
```


```{r, warning=FALSE, message=FALSE}
hm_token %>%
  mutate(score = abs(score), age = plyr::round_any(age+5, 10)) %>%
  group_by(age) %>%
  mutate(mean = mean(score)) %>%
  ggplot() + 
  geom_jitter(aes(x = factor(age), y = score), alpha = 0.06) + 
  geom_point(aes(x = factor(age), y = mean), color="red", shape="*", size = 7) +
  labs(x = "Range of Age", 
       y = "Scatter of scores")

hm_token %>%
  mutate(score = abs(score), age = plyr::round_any(age, 10)) %>%
  ggplot(aes(x = score, y = factor(age))) + 
  geom_density_ridges(aes(x = score, y = factor(age))) + 
  labs(x = "Density of scores", 
       y = "Range of Age")
```


```{r}
hm_tbl_re %>% 
  count(age, predicted_category) %>% 
  group_by(age, predicted_category) %>%
  summarise(percent = sum(n)) %>% 
  mutate(percent = percent/sum(percent)) %>%
  ggplot(aes(x = age, y = percent, fill = predicted_category)) + 
  geom_col(position = "stack", width=0.8)
```
```{r}
hm_tbl_re %>% 
  count(age, predicted_category) %>% 
  group_by(age, predicted_category) %>%
  summarise(percent = sum(n)) %>% 
  mutate(percent = percent/sum(percent)) %>%
  ggplot(aes(x = age, y = percent, color = predicted_category)) + 
  geom_line()
```

```{r}
burnin <- 500
iter <- 1000
keep <- 30

k <- 7

mods <- LDA(dtm, k, 
            method = "Gibbs",
            control = list(burnin = burnin,
                           iter = iter,
                           keep = keep))


```


```{r}
topics <- as.matrix(topics(mods))
terms <- as.matrix(terms(mods,10))
```


```{r}
# Find required quantities
phi <- as.matrix(posterior(mods)$terms)
theta <- as.matrix(posterior(mods)$topics)
vocab <- colnames(phi)
term_freq <- col_sums(dtm)

# Convert to json
json_lda <- createJSON(phi = phi, 
                       theta = theta,
                       vocab = vocab,
                       doc.length = as.vector(table(dtm$i)),
                       term.frequency = term_freq)

serVis(json_lda)
```

```{r}
# serVis(json_lda, out.dir = "doc", open.browser = FALSE)
```

```{r}
serVis(json_lda, out.dir = 'LDA_visual', open.browser = FALSE)
system("mv index.html results.html")
```

```{r}
temp <- hm_tbl_re %>% mutate(topics = topics)
```

```{r}
temp %>% 
  count(age, topics) %>% 
  group_by(age, topics) %>%
  summarise(percent = sum(n)) %>% 
  mutate(percent = percent/sum(percent)) %>%
  ggplot(aes(x = age, y = percent, fill = factor(topics))) + 
  geom_col(position = "stack", width=0.8)
```
```{r}
temp %>% 
  count(age, topics) %>% 
  group_by(age, topics) %>%
  summarise(percent = sum(n)) %>% 
  mutate(percent = percent/sum(percent)) %>%
  ggplot(aes(x = age, y = percent, color = factor(topics))) + 
  geom_line()
```

